\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-08 jss/article.tex
edit

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$). The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known. The efficiency of these priors is explored in the examples in section 5.

>>>>

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$). 
\\

The Poisson model can have such posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known. If $\lambda_0$ is unknown, the posterior distribution for the Poisson model is improper and this model should not be used. However, the Binomial model can still be used  instead because the Poisson distribution is just the approximation to the Binomial distribution. The efficiency of these priors is explored in the examples in section 5.
